%!TEX root = ../thesis.tex
% створюємо список використаної літератури
\begin{thebibliography}    
    \bibitem{KyberCCA}
       Joppe Bos, Léo Ducas and others. CRYSTALS – Kyber: a CCA-secure module-lattice-based KEM. ---  
        \newblock Cryptology ePrint Archive, Report 2017/634, 2017.  
        \newblock Режим доступу: \url{https://eprint.iacr.org/2017/634.pdf}.

    \bibitem{KyberWebsite}
        CRYSTALS-Kyber. Official website. ---  
        \newblock Режим доступу: \url{https://pq-crystals.org/kyber/}.

    \bibitem{babyKyber}
        Kyber - How does it work?: Post-Quantum Cryptography. Cryptopedia. ---  
        \newblock Режим доступу: \url{https://cryptopedia.dev/posts/kyber/}.

    \bibitem{Langlois2012}
        Langlois,~Adeline, Stehlé,~Damien. Worst-Case to Average-Case Reductions for Module Lattices. --- 
        \newblock Cryptology ePrint Archive, Paper 2012/090, 2012.  
        \newblock Режим доступу: \url{https://eprint.iacr.org/2012/090/20130815:054538}.

    \bibitem{Gonzalez2021}
        Gonzalez,~Ruben. Kyber - How does it work? ---  
        \newblock Approachable Cryptography, 2021.  
        \newblock Режим доступу: \url{https://cryptopedia.dev/posts/kyber/}.

    \bibitem{Lyubashevsky2013}
    Lyubashevsky,~Vadim, Peikert,~Chris, Regev,~Oded. On Ideal Lattices and Learning with Errors over Rings. ---  
    \newblock Journal of the ACM, vol.~60, no.~6, pp.~1--35, 2013.  
    \newblock Режим доступу: \url{https://doi.org/10.1145/2535925}.

    \bibitem{Langlois2012}
        Langlois,~Adeline, Stehlé,~Damien. Worst-Case to Average-Case Reductions for Module Lattices. ---  
        \newblock Cryptology ePrint Archive, Paper 2012/090, 2012.  
        \newblock Режим доступу: \url{https://eprint.iacr.org/2012/090/20130815:054538}.
    
    \bibitem{Pessl2017}
        Pessl,~Peter, Bruinderink,~Leon~Groot, Yarom,~Yuval. To BLISS-B or not to be - Attacking strongSwan’s Implementation of Post-Quantum Signatures. ---  
        \newblock Cryptology ePrint Archive, Paper 2017/490, 2017.  
        \newblock Режим доступу: \url{https://eprint.iacr.org/2017/490/20170828:125948}.
    
    \bibitem{Alkim2016}
        Alkim,~Erdem, Ducas,~Léo, Pöppelmann,~Thomas, Schwabe,~Peter. NewHope without reconciliation. ---  
        \newblock Cryptology ePrint Archive, Paper 2016/1157, 2016.  
        \newblock Режим доступу: \url{https://eprint.iacr.org/2016/1157/20171109:073050}.
    
    \bibitem{Avanzi2021}
        Avanzi,~Roberto, Bos,~Joppe, Ducas,~Léo, Kiltz,~Eike, Lepoint,~Tancrède, Lyubashevsky,~Vadim, Schanck,~John~M., Schwabe,~Peter, Seiler,~Gregor, Stehlé,~Damien. Algorithm Specifications and Supporting Documentation (version 3.02). ---  
        \newblock 2021.  
        \newblock Режим доступу: \url{https://pqc-hqc.org/doc/hqc-specification_2024-02-23.pdf}.
    
    \bibitem{Botros2019}
        Botros,~Leon, Kannwischer,~Matthias~J., Schwabe,~Peter. Memory-Efficient High-Speed Implementation of Kyber on Cortex-M4. ---  
        \newblock Cryptology ePrint Archive, Paper 2019/489, 2019.  
        \newblock Режим доступу: \url{https://eprint.iacr.org/2019/489/20190520:092623}.

    \bibitem{Lyubashevsky2024}
        Lyubashevsky,~Vadim. Basic Lattice Cryptography: The concepts behind Kyber (ML-KEM) and Dilithium (ML-DSA). ---  
        \newblock Cryptology ePrint Archive, Paper 2024/1287, 2024.  
        \newblock Режим доступу: \url{https://eprint.iacr.org/2024/1287/20241024:103131}.

    \bibitem{Kyber512NISTFAQ}
        FAQ on Kyber512. ---  
        \newblock National Institute of Standards and Technology (NIST).  
        \newblock Режим доступу: \url{https://csrc.nist.gov/csrc/media/Projects/post-quantum-cryptography/documents/faq/Kyber-512-FAQ.pdf}.

    \bibitem{KyberNISTRound3}
        CRYSTALS-KYBER Round 3 Official Comment. ---  
        \newblock National Institute of Standards and Technology (NIST).  
        \newblock Режим доступу: \url{https://csrc.nist.gov/csrc/media/Projects/post-quantum-cryptography/documents/round-3/official-comments/CRYSTALS-KYBER-round3-official-comment.pdf}.

    \bibitem{ScienceDirect2023}
        Yipei Yang, Zongyue Wang and others. Chosen ciphertext correlation power analysis on Kyber
        \newblock Future Generation Computer Systems, 2023.  
        \newblock Режим доступу: \url{https://www.sciencedirect.com/science/article/abs/pii/S0167926023000378}.

    \bibitem{KEMProof}
      Some KEMs and Some Proofs - Cronokirby---
        \newblock About - Cronokirby ---
        \newblock 2022. Режим доступу: \url{
          https://cronokirby.com/posts/2022/08/some-kems-and-some-proofs}.

    \bibitem{Campagna2020}
        Campagna,~Matthew. Security of Hybrid Key Establishment. ---
        \newblock Springer International Publishing, 2020.  
        \newblock Режим доступу: \url{
            https://www.amazon.science/publications/security-of-hybrid-key-encapsulation}.
    
 
\end{thebibliography}
